Computer Science House By-Laws

### 2016-11-07 bylaws.tex
New Packet
Freshmen get to try packet again before the end of their evaluation period.

After the second week of the Introductory Packet, Introductory Members who have received less than 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) will have their membership revoked.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet.
\end{enumerate}

>>>>

\end{itemize} \\
At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet. The results of this Introductory Packet may only affect the number of signatures evaluated at the Introductory Evaluation. 

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
